ASHA 2023 Listening Effort Data Analysis

### 2023-10-27 ASHA 2023 Analysis/data_analysis.Rmd
small change to analysis script
calculating mean speaker intel and repetition accuracy

## Phrase Accuracy

>>>>

## Speaker Intelligibility and Phrase Accuracy

### Mean Speaker Intelligibility

Across all trials in the study, the intelligibility level for each of the speaker is reported below.  Across listeners, the mean intelligibility for the ALS speaker was 81.08% with a standard deviation of 3.86. For the control speaker, the mean intelligibility level was 93.62% with a standard deviation of 2.90.

# Load in cleaned data

data <- rio::import("Cleaned Data/cleaned_data.csv")

intel_df <- data %>%
  dplyr::select(subject, trial, speaker, correct_words, target_number, rep_acc) %>%
  dplyr::distinct() %>%
  # removing trials with missing rep accuracy: 3 trials removed
  dplyr::mutate(rep_acc = ifelse(rep_acc == "", NA, rep_acc)) %>%
  dplyr::filter(!is.na(rep_acc))

intel_byListener <- intel_df %>%
  dplyr::group_by(speaker, subject) %>%
  dplyr::summarize(Intelligibility = sum(correct_words)/sum(target_number)*100)

intel_byListener %>%
  dplyr::group_by(speaker) %>%
  dplyr::summarize("Mean Intelligibility" = mean(Intelligibility), SD = sd(Intelligibility))

### Phrase Accuracy

# Calculating repetition accuracy descriptive data

rep_acc <- intel_df %>%
  dplyr::group_by(speaker, rep_acc) %>%
  dplyr::summarize(n = n()) %>%
  tidyr::pivot_wider(names_from = rep_acc,
                     values_from = n) %>%
  dplyr::mutate(percent_accurate = accurate/(accurate + inaccurate))
